\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
this makes the figures align better.
linda's edits through half the intro

Although Tor~\cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's anonymizing functionality also circumvented censorship. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor's network of unlisted relays and various methods of obfuscation making it a viable censorship circumvention tool even in the face of nation-state level adversaries.

To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool. We believe that this is a great opportunity for user research, both for investigating a case study of investigating the usability of a censorship circumvention tool, and also to help current Tor users censorship circumvention more easily. Not only will this allow for easier censorship circumvention, users who use Tor will be provided with extra security features that other censorship circumvention tools do not provide, such as anonymity. Additionally, increasing the adoption of Tor as a censorship circumvention tool benefits other users who use Tor as an anonymity system by increasing the number of overall users on the Tor network~\cite{dingledine2006anonymity}.

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
\caption{E2-OLD-X10-20160323-1400 attempted to download Tor Browser from TechSpot.com, but clicked on
a download link which was not from TechSpot.com. The download was from another site, 1download.io.}
\label{downloadio}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
\caption{E2-OLD-X28-20160328-1400 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
participant dutifully does before running the Tor Browser executable.}
\label{driverupdate}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
\caption{E1-OLD-X32-20160328-1400 downloaded Tor Browser from a legitimate Tor Browser mirror, \url{www.torservers.net/mirrors}.}
\label{mirror}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
\caption{E2-NEW-X21-20160323-1400 downloaded Tor Browser from TechSpot, clicking on the download link from 
TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
\label{techspot}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
\caption{E3-NEW-X11-20160330-1600 downloaded Tor Browser from Softsonic, a reputable-looking but
unconfirmed site.}
\label{softsonic}
\end{figure}

>>>>

Users started using Tor~\cite{dingledine2004tor} as a censorship circumvention tool because Tor's anonymizing functionality also coincidentally circumvented censorship. In fact, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}. Today, Tor is aware of these users and explicitly provides support for circumventing censorship through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and employs advanced techniques to resist blocking.

This is the first user study investigating the usability of Tor as a censorship circumvention tool. Our experiments are both a great a case study of observing users circumvent censorship, and a step to help current Tor users by making censorship circumvention easier. All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased the number of overall users on the Tor network~\cite{dingledine2006anonymity}.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
\caption{E2-OLD-X10-20160323-1400 attempted to download Tor Browser from TechSpot.com, but clicked on
a download link which was not from TechSpot.com. The download was from another site, 1download.io.}
\label{downloadio}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
\caption{E2-OLD-X28-20160328-1400 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
participant dutifully does before running the Tor Browser executable.}
\label{driverupdate}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
\caption{E1-OLD-X32-20160328-1400 downloaded Tor Browser from a legitimate Tor Browser mirror, \url{www.torservers.net/mirrors}.}
\label{mirror}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
\caption{E2-NEW-X21-20160323-1400 downloaded Tor Browser from TechSpot, clicking on the download link from 
TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
\label{techspot}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
\caption{E3-NEW-X11-20160330-1600 downloaded Tor Browser from Softsonic, a reputable-looking but
unconfirmed site.}
\label{softsonic}
\end{figure}
